The effects of host galaxy properties on merging compact binaries detectable by LIGO

### 2016-09-14 paper/mnras/paper.tex
update

We do not include specific prescriptions for metal distribution based on initial metallicity (such as for Population III stars) or variations in IMF.  }

>>>>

We do not include specific prescriptions for metal distribution based on initial metallicity (such as for Population III stars) or variations in IMF.  We cannot thus discuss Population III contributions to the gravitational wave background; however, studies by  \citet{Hartwig16}  and \citet{Dvorkin16} suggest that this contribution is fairly negligible.  We have shown that our scheme for metal production and distribution produces galaxies which match the mass-metallicity relation at $z \sim 3$ \citep{Brooks07} as well as in the local universe \citep{Christensen16}.  At higher redshifts, there is a very large spread in the metal distributions of damped Lyman alpha systems \citep{Dvorkin15}, suggesting that global galaxy metallicities depend on a wide range of parameter space.  Recently \citet{Hunt16a,Hunt16b} has presented {\bf depictions} of the mass-metallicity-star formation rate fundamental plane, which demonstrates an evolutionary relationship between these quantities.  {\bf we agree with the stuff}
}
